---
title: "Developing Data Products Course Project"
author: "Paul Venuto"
date: "3/19/2018"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Introduction

This presentation is the final project for the Coursera Developing Data Products course, which is part of the Data Science Specialization.

It is an R Presentation generated with RStudio.

The Shiny application pitched by this presentation is at https://pvenuto.shinyapps.io/rsconnect/

The Shiny app source code is available at 

## The Data

-The dataset used for this Shiny App was the Swiss Fertility and Socioeconomic Indicators (1888), which recorded standard fertility measures and socioeconomic indicators for each of 47 French-speaking provinces in Switzerland in 1888.

-The data frame consists of 47 observations on 6 variables, and this Shiny App focused on the relationship between 4 of those variables:

     -Fertility (Ig): common standardized fertility measure.
     -Agriculture: % of males involved in agriculture as occupation.
     -Examination: % draftees receiving highest mark on army examination.
     -Education: % education beyond primary school for draftees.

## Swiss Dataset

```{r swiss, message=FALSE}
library(UsingR)
library(ggplot2)
g = ggplot(swiss, aes(x = Agriculture, y = Fertility),)
g = g + xlab("Agriculture")
g = g + ylab("Fertility")
g = g + geom_point(size = 6, colour = "black", alpha = 0.2)
g = g + geom_point(size = 5, colour = "blue", alpha = 0.2)
g = g + geom_smooth(method = "lm", colour = "black")
g = g + ggtitle("Fitted Regression Line - Fertility vs. Agriculture")
g
```

## How The App Works

The app uses linear regression modeling to predict Fertility based on 3 predictors:

```{r, echo = TRUE, eval = FALSE}
library(shiny)
shinyServer(function(input, output) {
  model1 <- lm(Fertility ~ Agriculture, data = swiss)
  model2 <- lm(Fertility ~ Agriculture, Examination, data = swiss)
  model3 <- lm(Fertility ~ Agriculture, Examination, Education, data = swiss)
})
```

## Try it for yourself:

https://pvenuto.shinyapps.io/rsconnect/